---
title: "Example: First-Order Nitrate Removal in a Model Wetland"
author:
  - name: Ada Author
    corresponding: true
    email: ada.author@example.org
    affiliations:
      - name: Example Institute of Water Research
        country: Republic of Korea
abstract: |
  This example manuscript shows how wongo turns a Quarto source into journal-ready Word files.
  Every number in the text is computed from data by inline R code, so the text cannot drift from the analysis.
  Replace this abstract with your own.
keywords: [example, wongo, Quarto, reproducible manuscript, water treatment]
---

<!-- Writing rules (wongo):
     - ONE SENTENCE PER LINE. Never reflow; the DOCX round-trip depends on it.
     - Analysis numbers ONLY as inline R code, never typed by hand.
     - Cross-references only via @fig-/@tbl-/@sec-; citations only via @citekey. -->

```{r setup}
#| include: false
removal <- data.frame(
  day = 1:10,
  nitrate = c(12.1, 10.8, 9.9, 9.1, 8.2, 7.6, 7.1, 6.5, 6.0, 5.6)
)
fit <- lm(log(nitrate) ~ day, data = removal)
k <- -coef(fit)[["day"]]
```

# Introduction

Constructed wetlands remove nitrate from agricultural runoff [@kadlec2009].
This example estimates a first-order removal rate from ten days of synthetic data.

# Materials and Methods

We fitted a log-linear model to the daily nitrate concentrations (@fig-decay).

# Results and Discussion

The fitted first-order rate constant was `r sprintf("%.3f", k)` per day.
Nitrate fell from `r removal$nitrate[1]` to `r removal$nitrate[10]` mg/L over `r nrow(removal)` days (@tbl-data).

```{r fig-decay}
#| echo: false
#| fig-cap: "Nitrate concentration over time with the fitted first-order decay."
plot(removal$day, removal$nitrate, pch = 19, xlab = "Day", ylab = "Nitrate (mg/L)")
lines(removal$day, exp(predict(fit)))
```

```{r tbl-data}
#| echo: false
#| tbl-cap: "Synthetic nitrate concentrations."
knitr::kable(removal, col.names = c("Day", "Nitrate (mg/L)"))
```

# Conclusions

Replace this example with your manuscript and keep one sentence per line.

# Acknowledgments

This example uses synthetic data only.

# References

::: {#refs}
:::
